Equations for the sim

### 2021-01-27 sim_eq.tex
vertical controller

\section{Vertical dynamics}
\begin{equation}
	a_v = \frac{1}{m} (L - W),
\end{equation}
where $a_v$ is the vertical acceleration in ms$^{-2}$, $m$ is the mass of the aircraft in Kg, and $L$ and $W$ are the lift and weight forces respectively in Newtons.
\begin{equation}
W = mg,
\end{equation}
where $g = 9.8 \, \text{ms}^{-2}$ is the gravity acceleration.
\begin{equation}
L = c_l v_s^2,
\end{equation}
where $c_l$ is a coefficient to be determined experimentally, and $v_s$ is the airspeed of the aircraft. We can assume that
\begin{equation}
	v_s = c_{th}\, (t_h + \Delta t_h) + w_{bx},
\end{equation}
where $(t_h + \Delta_h) \in [0,100]$ is the throttle signal and $c_{th}$ is a coefficient to be determined experimentally, and $w_{bx}$ is the component of the wind vector along the horizontal axis of the vehicle. We set $t_h$ to a nominal value, let us say $50$ and we use $\Delta t_h$ to control the altitude of the aircrat with a P controller, i.e., 
\begin{equation}
	\Delta t_h = k_p (h_d - h_c),
\end{equation}
where $k_p$ is a positive gain constant, and $h_d$ is the desired altitude and $h_c$ is the current altitude of the aircraft in meters.

\subsection{Euler integration}
\begin{equation}
	\begin{cases}
		h(k+1) &= h(k) + v_s(k) \Delta T \\
		v_v(k+1) &= v_s(k) + a_v(k) \Delta T,
	\end{cases}
\end{equation}
where $v_v$ is the vertical speed (do not confuse it with the airspeed $v_s$).

\section{Horizontal dynamics}
\begin{equation}
	\begin{cases}
		\dot p &= c_{th}(t_h + \Delta t_h) \begin{bmatrix}\cos(\theta) \\ \sin(\theta) \end{bmatrix} + w \\
			\dot\theta &= u
	\end{cases},
\end{equation}
where $p$ is the position of the aircraft in the plane, $\theta$ is the angle of the velocity vector in the plane, $w$ is the wind vector, and $u$ is the control action for steering the aircraft (path tracking controller).

>>>>

\section{Vertical dynamics}
\begin{equation}
	a_v = \frac{1}{m} (L - W),
\end{equation}
where $a_v$ is the vertical acceleration in ms$^{-2}$, $m$ is the mass of the aircraft in Kg, and $L$ and $W$ are the lift and weight forces respectively in Newtons.
\begin{equation}
W = mg,
\end{equation}
where $g = 9.8 \, \text{ms}^{-2}$ is the gravity acceleration.
\begin{equation}
L = c_l v_s^2,
\end{equation}
where $c_l$ is a coefficient to be determined experimentally, and $v_s$ is the airspeed of the aircraft. We can assume that
\begin{equation}
	v_s = c_{th}\, (t_h + \Delta t_h) + w_{bx},
\end{equation}
where $(t_h + \Delta_h) \in [0,100]$ is the throttle signal and $c_{th}$ is a coefficient to be determined experimentally, and $w_{bx}$ is the component of the wind vector along the horizontal axis of the vehicle. We set $t_h$ to a nominal value, let us say $50$ and we use $\Delta t_h$ to control the altitude of the aircrat with a P controller, i.e., 
\begin{equation}
	\Delta t_h = k_p (h_d - h_c) - k_{vv} v_v,
\end{equation}
where $k_p$ and $k_{vv}$ are positive gain constants, $h_d$ and $h_c$ are the desired and current altitudes in meters respectively, and $v_v$ is the vertical velocity in m/s.

\subsection{Euler integration}
\begin{equation}
	\begin{cases}
		h(k+1) &= h(k) + v_s(k) \Delta T \\
		v_v(k+1) &= v_v(k) + a_v(k) \Delta T,
	\end{cases}
\end{equation}
where $v_v$ is the vertical speed (do not confuse it with the airspeed $v_s$).

\section{Horizontal kinematics}
\begin{equation}
	\begin{cases}
		\dot p &= c_{th}(t_h + \Delta t_h) \begin{bmatrix}\cos(\theta) \\ \sin(\theta) \end{bmatrix} + w \\
			\dot\theta &= u
	\end{cases},
\end{equation}
where $p$ is the position of the aircraft in the plane, $\theta$ is the angle of the velocity vector in the plane, $w$ is the wind vector, and $u$ is the control action for steering the aircraft (path tracking controller).
